Concurrent Programming with CXL

### 2020-07-03 book/paper.tex
Improved formatting
Latest

\newcommand{\cxlsource}[1]{
\begin{tabbing}
XX\=XXX\=XXX\kill
    \input{code/#1.tex}
\end{tabbing}
}

\newcommand{\cxllink}[1]{%
[\href{https://www.cs.cornell.edu/home/rvr/cxl/code/#1}{\underline{#1}}]%
}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/Up.py}
\end{code}
\caption{[Up.py] Python implementation of Figure~\ref{fig:inc}.}
\label{fig:incpy}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/UpMany.py}
\end{code}
\caption{[UpMany.py] Incrementing \texttt{N} times.}
\label{fig:incmany}
\end{figure}

@@

\section*{Exercises}
\begin{problems}
\item Implement an atomic swap operation.  It should take two pointer arguments
and swap the values.
\item Implement a spinlock using the atomic swap operation.
\item Write out the invariants that need to hold and check them using CXL.
\item People who use an ATM often first check their balance and then withdraw
a certain amount of money not exceeding their balance.  A negative balance
is not allowed.  Figure~\ref{fig:atm} shows two operations on bank accounts:
one to check the balance and one to withdraw money.
Note that all operations on accounts are carefully protected by a lock.
The \texttt{customer}
method models going to a particular ATM and withdrawing money not exceeding
the balance.  Method \texttt{checker} looks for negative balances.
Running the code through CXL reveals that there is a bug.
It is a common type of concurrency bug known as \emph{Time Of Check Time Of
Execution} (TOCTOE).
\index{Time Of Check Time Of Execution}
\index{TOCTOE}
In this case, by the time the withdraw operation is performed,
the balance can have changed.
\begin{enumerate}
\item Fix the code in Figure~\ref{fig:atm}.
\item Is it necessary to obtain a lock in \texttt{atm\_check\_balance()}?
\end{enumerate}
\end{problems}

>>>>

\newcommand{\cxlsource}[1]{
\begin{tabbing}
XX\=XXX\=XXX\kill
    \input{sources/#1.tex}
\end{tabbing}
}

\newcommand{\cxllink}[1]{%
[\href{https://www.cs.cornell.edu/home/rvr/cxl/sources/#1}{\underline{#1}}]%
}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../code/Up.py}
\end{code}
\caption{[Up.py] Python implementation of Figure~\ref{fig:inc}.}
\label{fig:incpy}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../code/UpMany.py}
\end{code}
\caption{[UpMany.py] Incrementing \texttt{N} times.}
\label{fig:incmany}
\end{figure}

@@

\section*{Exercises}
\begin{problems}
\item Implement an atomic swap operation.  It should take two pointer arguments
and swap the values.
\item Implement a spinlock using the atomic swap operation.
\item Write out the invariants that need to hold and check them using CXL.
\item People who use an ATM often first check their balance and then withdraw
a certain amount of money not exceeding their balance.  A negative balance
is not allowed.  Figure~\ref{fig:atm} shows two operations on bank accounts:
one to check the balance and one to withdraw money.
Note that all operations on accounts are carefully protected by a lock
(i.e., there are no data races).
The \texttt{customer}
method models going to a particular ATM and withdrawing money not exceeding
the balance.  Method \texttt{checker} looks for negative balances.
Running the code through CXL reveals that there is a bug.
It is a common type of concurrency bug known as \emph{Time Of Check Time Of
Execution} (TOCTOE).
\index{Time Of Check Time Of Execution}
\index{TOCTOE}
In this case, by the time the withdraw operation is performed,
the balance can have changed.
\begin{enumerate}
\item Fix the code in Figure~\ref{fig:atm}.
\item Is it necessary to obtain a lock in \texttt{atm\_check\_balance()}?
\end{enumerate}
\end{problems}
